Microscopy Data

### 2019-08-21 Microscopy Data.Rmd
added aggregate data from new thresholded images

#Isolate Sa

cleanResultsSa1 <- cleanResults1 %>% filter(Species == "Sa")
cleanResultsSaMono1<- cleanResultsSa1 %>% filter(Condition == "Sa Mono")

@@

GraphGrowthCurvesExpCleanCoCulture(cleanResultsStats)

>>>>

#Isolate Sa
cleanResultsSa1 <- cleanResults1 %>% filter(Species == "Sa")
cleanResultsSaMono1<- cleanResultsSa1 %>% filter(Condition == "Sa Mono")

@@

GraphGrowthCurvesExpCleanCoCulture(cleanResultsStats)
```
#This 
```{r new threshold images aggregates data}
GetAggregates<-function(sample, samplename){
  folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data1/',sample,'/aggregateSizes1')
  fileList<-list.files(path = folder, full.names = TRUE)
  growthDf<-data.frame()
  for (position in 0:5){
    currentPosition<-fileList[grep(paste0("p_",position,"."),fileList)]
    for (timepoint in 0:17){
      currentTimePoint<-currentPosition[grep(paste0("t_",GetNumber(timepoint),"p_"),currentPosition)]
      growthDf<-rbind(growthDf,ReadAggregateFile(currentTimePoint, position, timepoint))
      }
  }
  growthDf<-growthDf %>% mutate(Sample = samplename)
return(growthDf)
}

wtAggregates1<-MapAggregates(PA14wt, names3)
mutAggregates1<-MapAggregates(PA14mut, names3)
allAggregates<-bind_rows(wtAggregates1,mutAggregates1)
allAggregates<-allAggregates %>% filter(!Size<0.5)

ggplot()+
  geom_point(data = allAggregates)
  scale_y_log10(limits= c(1e4,1e7), name=expression(paste('Biomass from voxel counts' )), breaks = c(10^(seq(5,10,.5))), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  labs(title =expression(paste(italic("S. aureus"), " growth in mono in SCFM2" )),  x = "Time (hours)",shape = "Culture condition", color = "Antiobiotic/Control") 
```

```{r new threshold images aggregates graph}
TotalHistogram<-function(df){
  biomass<-df$Size
  totalbiomass<-sum(biomass)
  upperLim<-max(biomass)+5-mod(max(biomass),5)
  breaksSequence<-seq(0,upperLim,5)#this makes breaks every 100 pixels
  histogram<-data.frame()
  currentHist<-hist(biomass, plot = F, breaks = breaksSequence)
  histogram<-data.frame(currentHist$counts,currentHist$mids)
  colnames(histogram)<-c("Counts", "Midpoint")
  histogram<-histogram[!(histogram$Counts==0),]
  histogram%>%mutate(BiomassBin=Counts*Midpoint)->histogram
  histogram%>%mutate(NormBiomassBin=BiomassBin/totalbiomass)->histogram
  return(histogram)
}

testSplit<-split(allAggregates, c("Sa","Pa"))
allAggregates1<-allAggregates %>% filter(Species %in% c("Pa", "Sa"))
allAggregates$Strain<-as.factor(allData$Strain)
allAggregates$Sample<-as.factor(allData$Sample)
allAggregates$TimePoint<-as.factor(allData$TimePoint)
allAggregates$Position<-as.factor(allData$Position)

allData<-allAggregates %>% group_by(Species, Position, TimePoint, Sample, Strain)
yas<- group_split(allData)

ggplot()+
  geom_point(data = allAggregates, aes(x = TimePoint, y= Position, color = Sample, shape = Species))+
  facet_wrap(.~Strain)

plotHist3DBiomassCounts<-function(df1, title){
  ggplot()+
    geom_point(data=df1,aes(x=Midpoint, y=Counts, color = source))+
    scale_y_log10(name=expression(paste('counts' )), breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    xlab('Biomass (um^3)')+
    ylab('Counts')+
    ggtitle(paste0("Raw biomass Distribution (bin size = 10 um) ",title))
    #facet_wrap(~TimePoint, nrow=4)
  }
plotHist3DBiomassBinBiomass<-function(df1, title){
  ggplot()+
    geom_point(data=df1,aes(x=Midpoint, y=BiomassBin, color = source))+
    scale_y_log10(name=expression(paste('counts' )), breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    xlab('Biomass (um^3)')+
    ylab('Counts')+
    ggtitle(paste0("Raw biomass Distribution (bin size = 10 um) ",title))
    #facet_wrap(~TimePoint, nrow=4)
  }
plotHist3DBiomassNormBinBiomass<-function(df1, title){
  ggplot()+
    geom_point(data=df1,aes(x=Midpoint, y=NormBiomassBin))+
    #scale_y_log10(name=expression(paste('counts' )), breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    xlab('Biomass (um^3)')+
    ylab('Counts')+
    ggtitle(paste0("Raw biomass Distribution (bin size = 10 um) ",title))
    #facet_wrap(~TimePoint, nrow=4)
  }
